---
title: "Example 2"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lazyeval)
library(knitr)
library(testthat)
df <- readr::read_csv("sample_data_1.csv")
```

## Dplyr example 1

We have data that looks like this:

```{r}
knitr::kable(df)
```

I have included an 'expected distance' column so we can later do some unit tests

We can convert this into a tidy format as follows:

```{r}
df_c <- df %>% filter(id == "centroid")
df_p <- df %>% filter(id != "centroid")

suffixes = c(point="_p", centroid="_c")

df_d <- dplyr::left_join(df_p, df_c, by="cluster", suffix = suffixes) %>% 
  dplyr::select(-expected_distance_c, -cluster, -id_p, -id_c) %>% 
  dplyr::select(-dplyr::one_of("expected_distance_p"), dplyr::one_of("expected_distance_p")) %>% 
  dplyr::rename(expected_distance =expected_distance_p)
  
knitr::kable(df_d)
```

To compute a distance, we want pairs of vectors to put in a distance function like `distance(v1, v2)`.  We want v1 and v2 to be vectors of arbitrary length, corresponding to a set of columns that the user has selected  

```{r}
distance_cols <- c("x", "y")
point_cols <- paste0(distance_cols, suffixes["point"])
centroid_cols <- paste0(distance_cols, suffixes["centroid"])


# Convert columns into a list of vectors, each element of which aggregates the
# nth element of the columns into a vector.  Similar to `zip` in Python
cols_to_list_of_vectors <- function(...) {
  arguments <- list(...)
  combine <- function(...) {
    arguments = list(...)
    unlist(arguments)
  }
  purrr:::pmap(arguments, combine)
}


```

```{r}
args_p <- purrr::map(point_cols, as.name) #Note this args thing contains symbols - see typeof(args[[2]])
f_point <- ~ cols_to_list_of_vectors(uqs(args_p))  #Note this is a formula, as signified by ~ 

args_c <- purrr::map(centroid_cols, as.name)
f_centroid <- ~ cols_to_list_of_vectors(uqs(args_c))  #Note this is a formula, as signified by ~  

df_d <- df_d %>% 
  mutate_(v_p = f_interp(f_point)) %>% 
  mutate_(v_c = f_interp(f_centroid))

kable(df_d)
```


Apply our distance function:

```{r}

get_dist <- function(v1, v2) {
    as.double(dist(rbind(v1, v2)))
  }

df_d <- df_d %>% 
  mutate(distance = purrr::map2_dbl(v_p, v_c, get_dist))

kable(df_d)


```

Check that it gives the right result:

```{r}
testthat::expect_true(all.equal(df_d$expected_distance, df_d$distance))
```



